Fusing Filters with Integer Linear Programming

### 2014-05-15 2014betterfusionforfilters/Main.tex
abstract wording

\begin{abstract}
Minimising memory traffic is key to compiling functional, collection oriented array programs into efficient code. To achieve this, it is not sufficient to just fuse subsequent array operations into a single, more complex computation, we also have to also \emph{cluster} separate traversals of the same array into one single loop. Previous work demonstrated how Integer Linear Programming (ILP) can be used to cluster the operators in a general data-flow graph into subgraphs, which can be individually fused. However, these approaches have one serious restrictions: they can only handle operations which preserve the size of the array, thereby missing out on some optimisation opportunities. The technique we present in this paper addresses this shortcoming by extending the ILP approach with support for size-changing operations, using an external ILP server to find good clusterings.

>>>>

\begin{abstract}
Minimising memory traffic is key to compiling functional, collection oriented array programs into efficient code. To achieve this, it is not sufficient to just fuse subsequent array operations into a single, more complex computation; we also have to \emph{cluster} separate traversals of the same array into one single loop. Previous work demonstrated how Integer Linear Programming (ILP) can be used to cluster the operators in a general data-flow graph into subgraphs, which can be individually fused. However, these approaches have one serious restriction: they can only handle operations which preserve the size of the array, thereby missing out on some optimisation opportunities. The technique we present in this paper addresses this shortcoming by extending the ILP approach with support for size-changing operations, using an external ILP solver to find good clusterings.
